Magnetic Inhibition of Convection and the Fundamental Properties of Low--Mass Stars

### 2016-03-08 paper/ms.tex
continuing the discussion

{\bf Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrones traces a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K. This suggests that magnetic inhibition plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars is relatively insensitive to the influence of magnetic fields. In between these two regimes, the models predict a transition in which stars appear to exhibit an increasing sensitivity to magnetic inhibition of convection as effective temperature decreases. }

{\bf As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that a similar transition occurs over roughly the same effective temperature domain in the empirical HR diagram of Upper Scorpius. Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6\,000$~K) are best described by a 10 Myr standard stellar model isochrone. Instead of continuing to follow a 10 Myr standard model isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr causing the empirical sequence to exhibit a shallower slope than standard model predictions between $5\,750 > T_{\rm eff} / {\rm K} > 4\,500$. 
That the shallower slope in the empirical HR diagram and the transition predicted by magnetic stellar models are coincident, suggests that the two phenomena may be connected.
}

@@

{\bf The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$. Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope. In the absence of a convective envelope, magnetic inhibition of convection is irrelevant. Therefore, any differences observed between magnetic and standard stellar model isochrones at this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases. This provides a natural explanation for the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone that occurs near this effective temperature in Fig.~\ref{fig:ages}(b). 
It then seems reasonable to posit that the shallow slope of the empirical HR diagram and the observed transition in the magnetic models trace the demise of outer convective envelopes and the growth of radiative cores in young, pre-main-sequence stars.}

@@

{\bf While this behavior is expected in the magnetic models, it does not need to necessarily correspond to the observed transition. General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism responsible for the age discrepancy between the high- and low-mass stellar populations. However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism with the models failing to reproduce the precise morphology at the magnetic sequence turn-off.}

>>>>

{\bf Figure~\ref{fig:ages} shows that a 10 Myr magnetic model isochrone agrees with predictions from a 5 Myr standard model isochrone for effective temperatures below about 5\,000~K, but traces a 10 Myr standard model isochrone above 6\,000~K. This suggests that magnetic inhibition of convection plays an important role in dictating the structure of cool low-mass stars, but the structure of warmer high-mass stars is relatively insensitive to the influence of magnetic fields. In between these two regimes, models predict a transition in which stars appear to exhibit a decreasing sensitivity to magnetic inhibition of convection as effective temperature increases. }

{\bf As was noted in Sect.~\ref{sec:results}, Figs.~\ref{fig:empirical} and \ref{fig:ages}a indicate that a similar transition occurs over roughly the same effective temperature domain in the empirical HR diagram of Upper Scorpius. Early- to mid-G stars in Upper Scorpius (\teff$ \sim 6\,000$~K) are best described by a 10 Myr standard stellar model isochrone. Instead of continuing to follow a 10 Myr standard model isochrone, late-G stars appear to be better represented by an isochrone intermediate between 5 and 10 Myr. This causes the empirical sequence to exhibit a shallower slope than standard model predictions between $5\,750 > T_{\rm eff} / {\rm K} > 4\,500$. 
That the shallower slope in the empirical HR diagram and the transition predicted by magnetic stellar models are coincident, suggests that the two phenomena may be connected.
}

@@

{\bf The transition exhibited by theoretical magnetic models can be explained by a rapid thinning of outer convective envelopes in stars with masses above about 1.2 $M_{\odot}$ \citep[e.g.,][]{Iben1965}. Once a star reaches an effective temperature of 6\,000 K, it has a very small or non-existent convective envelope, independent of whether or not magnetic inhibition of convection is considered. In the absence of a convective envelope, magnetic inhibition of convection is irrelevant. Therefore, any differences between magnetic and standard stellar model isochrones above this effective temperature are the result of the magnetic field's influence on stellar structure at earlier evolutionary phases (i.e., delayed contraction). This naturally explains the convergence of the 10 Myr magnetic isochrone with the 10 Myr standard model isochrone, which occurs near $6\,000$~K in Fig.~\ref{fig:ages}(b). 
It then seems reasonable to posit that the shallow slope of the empirical HR diagram traces the demise of surface convection zones, the weakening of surface magnetic dynamo action, and the growth of radiative cores in young, pre-main-sequence stars.}

@@

{\bf While this behavior is expected in the magnetic models, it does not need to necessarily correspond to the observed transition. General agreement between the behavior of the magnetic model isochrone and the observed stellar locus provides evidence that magnetic inhibition of convection is the mechanism responsible for the age discrepancy between the high- and low-mass stellar populations. However, it is clear that this statement only holds with respect to the plausible identification of a general mechanism as the models fail to reproduce the precise morphology at the magnetic sequence turn-off.}
